---
title: "Observer sampling of Chinook"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(here)
```

```{r readData}
sqdat <- readRDS("data/squash_data.RDS")
```

I created a “samplenum” field which is just a dummy for each row with a non-NA specimen_number. I think this should end up just being the number of rows in each year. 

```{r create function for summarizing data}
obsfun <- function(sample){
  dots <- enquo(sample)
  sqdat %>% 
    select(area,year,!!dots) %>% # Search help files for "quasiquotation" to explain '!!'
    filter(!is.na(!!dots)) %>% 
    group_by(area,year) %>% 
    count(!!dots) %>% 
    spread(area,n)
}
```

Pre-2008:
Any fish with a row in “obsint.debriefed_age_squash_sp_type” (i.e., these data) should have been checked for an adipose fin.  So this should be our proxy for the number of fish “observed.” *Supposedly* any fish that was “observed” and did not have an adipose, should have been “sampled” (i.e., snout collected if missing an adipose). The key here though is that, among these fish that were checked for adipose fins, we don’t know how many snouts were collected. 

Can we assume that the fraction of clipped fish in the sampled population has remained constant through time, thereby using more recent clipped fractions as a proxy for the number of snouts actually collected? I dunno.

So the general idea here:
Assume that if a fish was clipped, it was tagged.
Assume that if we have a sample record for a fish in the squash table, it was checked for an adipose.

Tally squash records and determine the NMFS area for each. Based on NMFS area, assign to a fleet. 


Okay, so our maximum possible number of fish that were checked for a CWT would be from this table.
```{r}
obsfun(samplenum) %>%  dplyr::select(-samplenum) %>% data.frame #This should be our proxy for fish that were "observed" but this doesn't tell us if they had an adipose. 
```

Theoretically (*I think*) that any fish with a samplenum (above) should appear in the sex_length_weight query below. That's not necessarily the case though. Sigh. I think we still just use the values from the above table. 

```{r}
obsfun(type_3_sex_length_weight)
```

Below are some summaries of different tissue sample collections. 

```{r}
obsfun(type_4_fin_clips)
```

From 2011-2013, snouts were recorded as "type_11_other_tissue"

```{r}
obsfun(type_11_other_tissue)
```

From 2014-2019 snouts were recorded as either type_11_other_tissue or type_12_snout

```{r}
obsfun(type_12_snout)
```

```{r}
obsfun(type_13_adipose_present)
```

